SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] wrapping up libsubmarine

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties for Ethereum smart contracts: (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.

% Jeremy: Merge this into the caption so there is one stand-alone description
%With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover. By \textsf(1) funding the \textit{commitment address}, user is committed to the unlock transaction. In the reveal phase, \textsf(2) user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction. \textsf(3) Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. \textsf(4) Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{libsubmarine,submarinesendHD} extend the confidentiality of the commit and reveal, so that the commitment transaction is identical to a transaction to a newly generated Ethereum address. (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract. See Figure~\ref{fig:LibSubmarine}.
